The realization of this thesis wouldn't be possible without the presence of
many people who are dear to me. Without Sonja's presence and
constant support, especially at moments of weakness, life would have been
much more difficult. The time I spent in Osnabr\"uck would have
been only half an experience without you. I would like to express my indebtedness to my
supervisor Peter K\"onig, for his always friendly face, supportive
behavior, liberal attitudes, the scientific freedom he gives to his
students, and most importantly for creating a working environment that is
both friendly and scientifically outstanding at the same time (two
qualities rarely simultaneously present). Starting from a single room with
a laser printer, building up into a real lab was a most special experience.
I would like to also thank my second supervisor Dirk Jancke for the
experiments he conducted in Bochum, for his always supporting, friendly
attitude and patience. This path was made even more interesting thanks to
many friends and colleagues who accompanied me all along. Alper
A\c{c}{\i}k was a precious companion always eager to hold brain-storming
sessions and interesting discussions; Cliona Quigley had for me an immense
patience for being obliged to listen and correct my horrible written and
spoken English mistakes; without Daniel Weiller complex questions would
have never been solved so easily, he was always ready to give the good
answer; without Johannes Steger it would have not been possible to harbor
any positive feelings about Unix based computers and their terminals. I
would like to thank also Nora Nortmann, Frank Schumann, Lina Jansen,
Wolfgang Einh\"auser-Treyer, Saskia Nagel, Boris Bernhardt, Klaus Libertus,
Hans-Peter Frey and Sonja Engmann in the NBP group for all their positive
presence and professional contributions. A little further away J\"org Hipp,
Christoph Kayser, Gudrun Moeller, Rodrigo Salazar, Konrad K\"ording were
helpful colleagues during the first year I spent at INI in ETH Z\"urich. I
would like to thank also distant friends Florian Rigault, Yann Cojan,
Manuel Mercier. A big thanks to Jacqueline Griego who has proofread parts
of my thesis and Wolfgang Einh\"auser-Treyer who accepted to be one of the
reviewers of my thesis. Finally I own a big debt of gratitude to my parents who
supported me during all my studies. I can not thank them enough for the
love they give me.\\ \\ \\ 

