\begin{center}

\Large{\textsc{Selim Onat}}
\end{center}
%\vspace{1\baselineskip}


\section*{Personal Details}
\begin{flushleft}
  \textbf{Gender:} Male \\
  \textbf{Date of birth:} 19\textsuperscript{th} of October, 1978\\
  \textbf{Place of birth:} Istanbul, Turkey \\
  \textbf{Present Citizenship:} Turkish \\
  \textbf{Languages:} Turkish (native), French (near native), English (near
  native), (German  basics)\\
  \textbf{Address:} Albrechtstr. 28, 49069 Osnabr\"uck Germany\\
  \textbf{Phone:} +49 541 969 3509 \\
  \textbf{Fax:} +49 541 969 2596 \\
  \textbf{Email:} sonat@uos.de \\
  \textbf{Homepage:} www.selimonat.com\\
  \textbf{Other working experience:} Visual Artist, residential VJ in a local night
  club. Volleyball Player. \end{flushleft}

\section*{Publications\footnote{Publications which are included in this
thesis are marked with an asterisk.}} 


\textbf{Where do Humans Look at during Scanning of Natural Images: A
Comparison of High- vs. Low-Level Features.} Selim Onat, Alper A\c{c}{\i}k,
Frank Schumann, Peter K\"onig (in Preparation)

\textbf{*Processing of Locally Presented Natural Movies and Contextual
Interactions under Natural Conditions.} Selim Onat, Peter K\"onig, Dirk
Jancke (in Preparation)


\textbf{*Processing of Natural Movies Revealed by Voltage-Sensitive Dye
Imaging Across Primary Visual Cortex. } Selim Onat, Peter K\"onig, Dirk
Jancke (2009, Submitted) \textit{PLOS Biology}


\textbf{*Multiplexing information about position and orientation in early
visual cortex: A voltage-sensitive dye imaging study.} Selim Onat, Peter
K\"onig, Dirk Jancke (2009 Submitted) \textit{PNAS}


\textbf{*Visual stimulus locking of EEG is modulated by temporal congruency of
auditory stimuli.} Sonja Schall, Cliodhna Quigley, Selim Onat, Peter
K\"onig (2009) \textit{Exp Brain Res}

\textbf{Saliency on a natural scene background: Effects of color and luminance
contrast add linearly.} S. Engmann, T. Sieren, S. Onat, P. K\"onig and W.
Einh\"auser (2009) \textit{Attention, Perception \& Psychophysics} 


\textbf{Effects of contrast and its modification on fixation behavior
during free viewing of images from different categories.} Alper A\c{c}{\i}k, Selim
Onat, Frank Schumann, Peter K\"onig (2009) \textit{Vision Research}

\textbf{How does binocular disparity information influence overt attention.}
Lina Jansen, Selim Onat, Peter K\"onig (2009) \textit{Journal of Vision}

\textbf{Audio-visual integration during overt visual attention.} Cliodhna
Quigley, Selim Onat, Sue Harding, Martin Cooke, Peter K\"onig (2008)
\textit{J of Eye Movement Research}


\textbf{*Integrating audio-visual information for the control of overt
attention.} Selim Onat, Klaus Libertus, Peter K\"onig (2007) \textit{Journal
of Vision}

\textbf{Phasic activation of locus coeruleus neurons by the central nucleus
of the amygdala.} Bouret S, Duvel A, Onat S, Sara SJ (2003) \textit{J
Neuroscience}

\section*{B.Sc. \& M.Sc. Theses Supervised }

\textbf{B.Sc. Theses}

\textbf{Quantitative Analysis of Stable Representations of 
Disparity in Natural Visual Images} by Thesis Sebastian Bitzer

\textbf{Quantitative Properties of Sparse Binocular Representations of
Natural Visual Images} by Thesis Markus Goldbach 

\textbf{Cross-modal Integration of Natural Visual and Auditory Stimuli}
by Thesis Klaus Libertus

\textbf{The Influence of 2nd Order and Higher Order Correlation in Natural
Visual Stimuli on Human Overt Attention} by Thesis Sonja Schall

\textbf{Effects of higher order luminance structure on the 
selection of fixation points} by Thesis Swantje Nadler

\textbf{Investigation into Differences of Monkey and Human Eye Movements}
by Thesis Benjamin Auffarth 

\textbf{How Disparity fits into the Statistics and the Neural Processing of
Natural Scenes. An EEG Study} by Thesis Boris Bernhardt

\textbf{Human Eye Movements in Three Dimensional Natural Scenes} by
Thesis Lina Jansen

\textbf{Baseline Study on Overt Visual Attention} by Thesis Anke Walter

\textbf{A Comparison of Gaze Direction and Subjectively Interesting Points
During Free Viewing of Visual Scenes} by Thesis Moritz Lehne 

\textbf{Left-Right Asymmetry in Overt Attention} by Sarah Mieskes

\textbf{Integration of Luminance Contrast and Colour Contrast in Directing
the Human Gaze} by Sonja Engmann

\textbf{Investigation into Differences of Monkey and Human Eye Movements}
by Benjamin Auffarth

\textbf{M.Sc. Theses}

\textbf{Effects of Contrast and its Modifications on Fixation Behavior 
During Free Viewing of Images from Different Categories} by Thesis Alper
A\c{c}{\i}k 

\textbf{Influence of 3D Natural Stimuli on Eye Movements and the Selection
of Fixation Points} by Thesis Lina Jansen

\textbf{Integration of Different Features in Guiding Eye-Movements} by
Thesis Frank Schumann 

\textbf{Audiovisual Integration of Natural Stimuli for the Control of Overt
Attention} by Cliodhna Quigley

\textbf{Amplitude Locking of EEG Activity to Dynamic Audiovisual
Stimuli} by~Thesis~Sonja~Schall 

\section*{Teaching Experience}

\textbf{Winter Term 2003/2004:} Neurobiology of Learning 

\textbf{Summer Term 2003/2004:} Neural Coding (based on Dayan and Abbott's
Theoretical Neuroscience)

\textbf{Winter Semester 2004/2005:} Numerical Analysis in Neuroscience

\textbf{Winter Semester 2007/2008:} Neural Coding

\section*{Education}
\textbf{2004-present}\\ 
PhD in the Cognitive Science Program at University of
Osnabr\"uck, (Germany), under the supervision of Prof. Dr. Peter K\"onig

\textbf{2002-2003}\\
First year of PhD in Institute of Neuroinformatics,
ETH/Z\"urich (Switzerland) under the supervision of Dr. Peter K\"onig.  

\textbf{2001-2002}\\
M.Phil. (DEA, Diplome d'\'etudes approfondies) in Cognitive Science,
Universit\'e Pierre \& Marie Curie (Paris, France). Thesis (\textit{\'Etude
\'electrophysiologique de l'interaction fonctionnelle entre le Complexe
Amygdalien et le Locus Coeruleus}) accomplished in the Laboratory of
Neuromodulation and Memory Processes (Institut de Neuroscience, CNRS) under
supervision of Dr. Susan Sara.  

\textbf{2000-2001}\\
M.Sc. (Ma\^itrise) in Cellular Biology and Physiology (Specialization:
Neurosciences), University d'Orsay (Paris, France).

\textbf{1997-2000}\\ 
B.Sc. (DEUG + Licence) in  Biology (Specialization: Cellular Biology and
Physiology), University of Rennes 1 (France).


\textbf{1996-1997}\\ 
High School Diploma, French College St. Beno\^it, Istanbul (Turkey).

%\pagebreak

\section*{References}

\noindent These persons are familiar with my professional qualifications and my character:
\\

\textbf{Prof. Dr. Peter K\"onig } \\
Thesis supervisor \\
Email:  pkoenig@uos.de \\ 
Phone:  +49 541 969 2399 \\
Fax:    +49 541 969 2596 \\
Address: Osnabr\"uck University \\
Institute of Cognitive Science \\
Albrechtstr. 28, 49069  Osnabrueck Germany \\

\textbf{Dr. Dirk Jancke }\\
Thesis 2\textsuperscript{nd} supervisor \\
Email:  jancke@neurobiologie.rub.de \\
Phone:  +49 234 32 27845\\
Ruhr-University Bochum\\ 
Institut f\"ur Neuroinformatik \\
ND 03/70 44780 Bochum, Germany \\

\textbf{Dr. (Emerita) Susan Sara }\\
M.Sc. Thesis Supervisor\\ 
Email:  susan.sara@college-de-france.fr \\
Phone:  +33 1 44 27 14 15\\
Coll\`ege de France \\
Laboratoire de Physiologie \\de la Perception et de l'Action \\
11, place Marcelin Berthelot \\
75231 Paris Cedex 05\\



